% Define document class
\documentclass[twocolumn]{aastex631}
\usepackage[ruled,vlined,linesnumbered]{algorithm2e}
\usepackage{algorithmic}
\usepackage{color}
\usepackage{booktabs}
\usepackage{xspace}
\usepackage{orcidlink}

\graphicspath{{./figure/}}

\newcommand{\jhu}{\affiliation{Department of Physics and Astronomy, Johns Hopkins University, 3400 N. Charles
Street, Baltimore, MD 21218, USA}}

\definecolor{rb4}{HTML}{27408B}

\newcommand{\kw}[1]{{\color{rb4}[KW: #1 ]}}
\newcommand{\fill}[1]{{\color{red}[FILL: #1 ]}}

\begin{document}

\title{A computational model for the hinge moment in high jump}

\author{Eli Gitter-Dentz$^*$}
\jhu
\author{Elia Janes$^*$}
\jhu
\author{Kaze W. K. Wong \orcidlink{0000-0001-8432-7788}}
\jhu
%\email{kazewong@jhu.edu}
%

\footnote{$^*$ Equal contribution}
\date{\today}

\begin{abstract}
We employ two simple computational models to understand the biomechanics of high jump.
We find xxx
\end{abstract}


%\tableofcontents

%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{sec:intro}

% Most study in high jump has been emprical
There have been many empirical studies based on clinical trials \cite{WILSON20112207, MateosPadorno2021KinematicAO, }.

\cite{Sado2021CurvedAI,Fujimori2024JointKD}

The rest of this paper is organized as follow:
In Section \ref{sec:method}, we describe the tools we use to construct the high jump models and the assumptions going into the models.
In Section \ref{sec:results}, we show the experiment results.
In Section \ref{sec:discussion}, we discuss the implications of our results and future directions.

\section{Simulation models}
\label{sec:method}


To simulate the target systems, we employ \textsc{MuJoCo} \cite{todorov2012mujoco} as the underlying engine. 
\textsc{MuJoCo} (Multi-Joint dynamics with Contact) is a physics engine designed for the simulation and control of complex dynamical systems with contacts, constraints, and articulated bodies.
On top of being a physics engine, \textsc{MuJoCo} supports modern features such as differentiable simulation and GPU acceleration.
Because of these features, it is widely used in robotics research and has been the backbone of many state-of-the-art machine learning studies and applications in robotics, such as reinforcement learning and direct control.\cite{1606.01540,mujoco_playground_2025, towers2024gymnasium, Schulman2017ProximalPO}.



% We choose two simpler model for interpretable results.
While it is possible to integrate a full musculoskeletal model in Mujoco, the complexity of such a model makes it difficult to interpret the results.

We construct two simple models to understand the zeroth order and first order effects in high jump instead. The first model is a rigid stick model, which is a simple model of a rigid rod entering at an angle with a certain velocity. This model gives us insight on how the basic kinematics variable such as incident angle, lean angle, and initial velocity affect the resulting height. The second model is a multi-segment model aims to represent an oversimplified version of the human body. Building on top of the understanding from the first model, we aim to use this model to investigate the criteria for optimal kinematic chain activation.

\subsection{Rigid stick model}

% Define the model and its parameters

This basic models consists of two components: a rigid stick and a high jump pit. 

We list the parameters of the rigid stick model in Table \ref{tab:stick_parameters}.
\begin{table}[hbt!]
    \begin{center}
    \begin{tabular}{ l l }
    \hline
    \hline
    Parameter &  Description \\
    \hline

    $L$ & Length of the stick \\
    
    \hline
    \hline
    \end{tabular}
    \caption{}
    \label{tab:stick_parameters}
    \end{center}
\end{table}

\subsection{Multi-segment model}

% Define the model and its parameters
The additional parameters of the multi-segment model are listed in Table \ref{tab:stick_parameters}.
\begin{table}[hbt!]
    \begin{center}
    \begin{tabular}{ l l }
    \hline
    \hline
    Parameter &  Description \\
    \hline

    $L$ & Length of the stick \\
    \hline
    \hline
    \end{tabular}
    \caption{}
    \label{tab:ms_parameters}
    \end{center}
\end{table}

\section{Experimental Results}
\label{sec:results}

With the two models defined in Section \ref{sec:method}, we perform a series of three experiments to investigate key factors affecting the take off of high jump.

\subsection{Optimal approach angles}

The first experiment aims to find the correlation between the approach angle and the resulting height.
A curved approach has been the standard technique in high jump from beginner to elite level. The curve approach offers a number of advantages over a straight line approach, such as creating angular momentum for rotation over the bar and reducing forces exterted onto joints \cite{Tan1997TheMO, Tan01012005, Sado2021CurvedAI}.
However, the curve approach also introduces additional complexity to the jump, most noticeably the need to coordinate an inward lean with the approach angle.
While there has been reports and studies on the angles used by professional athletes \cite{Nicholson2024DifferencesIR}
% Describe the range of parameters

\subsection{Force distribution in multi-segment model}

The next experiment extends the first experiment to investigate the force demand on joints in the multi-segment model.


\subsection{Kinematic chain activation}

\section{Discussion}
\label{sec:discussion}

% Investigate the effect of flop

% Employ full body biomechanical model

\bibliography{HJModel}

%%%%%%%%%%%%%%%%%%%%%%
\end{document}
